About

### 2021-02-19 analysis/about.Rmd
workflowr::wflow_publish("analysis/about.Rmd")

## Read the code, access the data

@@

## Install the R package

@@

Please note that this project was built with R version 3.6.1 on a CentOS 7 operating system.
Some packages from this project **are not compatible with R versions prior version 3.6.0.**

@@

>>>>

## Reading the code, accessing the data

@@

## Installing the R package

@@

Please note that this project was built with R version 4.0.3 on a CentOS 7 operating system.
Some packages from this project **are not compatible with R versions prior version 3.6.0.**

@@

## Creating targets with {drake}

Calling `r_make()` will create targets specified in `drake_config(targets = <target>)` in `_drake.R` with the additional drake settings specified.

Out of the 400+ targets in this project, the following targets are important:

-   `bm_aggregated_new_buffer2`: Aggregated benchmark results of all models using a 2 meter buffer for hyperspectral data extraction.
-   `eda_wfr`: Creates the [report which shows Exploratory Data Analysis (EDA) plots and tables](https://pat-s.github.io/2019-feature-selection/eda.html).
-   `eval_performance_wfr`: Creates the [report which evaluates the model performances](https://pat-s.github.io/2019-feature-selection/eval-performance.html).
-   `spectral_signatures_wfr`: Creates the [report which inspects the spectral signatures of the hyperspectral data](https://pat-s.github.io/2019-feature-selection/spectral-signatures.html).
-   `feature_importance_wfr`: Creates the [report which inspects the feature importance of variables](https://pat-s.github.io/2019-feature-selection/feature-importance.html).
-   `filter_correlations_wfr`: Creates the [report which inspects correlations among filter methods](https://pat-s.github.io/2019-feature-selection/feature-importance.html).

Note that most reports require some/all fitted models.
Creating these (e.g. target `benchmark_no_models_new_buffer2`) is a costly process and takes several days on a HPC and way longer on a single machine.
